Water discharge has a variable impact on sediment transport capacity in subglacial systems

### 2023-08-11 Delaneyetal2023b.tex
merged and updated

\subsection{Role of water discharge in sediment transport capacity}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{Fig2.pdf}
  \caption{Model outputs resulting from the hydrographs shown in panels a and e for the cases called \alpine (a-d) and \icesheet{} (e-h).". Gray (black) lines in a and e represent the subglacial channel size (water discharge).  In other panels, blue lines represent model outputs from the subglacial channel, while orange lines represent the subaerial channel.
    Data in plots are at $15$\unit{min} intervals.
    Arrows denote some events where the variable peaks in the subglacial channel prior to the subaerial one.
    Insets in e-h show the  peak melt event \icesheet{} denoted by shaded area.
    Note that the x and y axis are different for \alpine{} and \icesheet{} such that they each cover a summer.} 
  \label{fig:model_outs}
\end{figure}
Following the parameterizations defined in Sections~\ref{sect:sub_mode}~and~\ref{sect:fluv}, the water velocity, shear stress, and width-integrated shear stress exhibit different seasonal evolutions and peaks. Water velocity and shear stress represent the potential for sediment mobilization, and width-integrated shear stress represents the total sediment transport capacity across the channel bed (Figure~\ref{fig:model_outs}).

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{Fig3.png}
  \caption{Relationship between water discharge and velocity, shear stress, and width-integrated shear stress for \alpine{}  (a-c) and \icesheet (d-f). Variables have been normalized to mean values for better comparison amongst the model runs.
    $R_g$ ($R_f$) show the Spearman rank correlation values for the subglacial (subaerial) model outputs.
    Plots are shown at $15$\unit{min} interval.} 
  \label{fig:Qw_vari}
\end{figure}

@@

\begin{figure}[h]
  \centering
    \includegraphics[width=0.8\linewidth]{Fig4.png}
    \caption{Variance (measured by the standard deviation) in water velocity, shear stress and total shear stress for different time aggregations across a large number of subglacial and subaerial channel shapes and friction factors The subglacial (blue) and subaerial (orange) systems are distinguished as are \alpine{} (a-c) and \icesheet{} (d-f).
      Shaded areas denote the $25^{\mathrm{th}}$ and $75^{\mathrm{th}}$ quantiles of the $100$ parameter combinations tested for each of the systems (Section~\ref{sect:imp}).
      Solid lines denote  mean values.
      Time intervals shown with markers denote $15$\,\unit{min}, $1$\,\unit{hr}, $12$\,\unit{hr}, $1$\,\unit{d}, $5$\,\unit{d}, $10$\,\unit{d}, and $15$\,\unit{d} aggregation periods.
    } 
    \label{fig:multi_run}
  \end{figure}

@@

Considerations in interpretations of sediment discharge should be made given the findings presented here.
These considerations include:
\begin{enumerate}
\item the inconsistent relationship between water discharge and sediment transport capacity underneath glaciers;
\item the timing of peak sediment transport capacity below glaciers can occur when the rate of change in water discharge is large, as opposed to the maximum quantity of water discharge;
\item the potentially increased variability in sediment discharge from underneath glaciers than in rivers they feed;
\item the representations of water discharge such as subglacial sediment transport capacity, subglacial sediment access, or open channel processes near the glacier margin in sediment records collected near glaciers. 
\end{enumerate}

@@

\renewcommand{\figurename}{Figure S}
\setcounter{figure}{0}
\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig2_hr.png}
    \caption{As Figure \ref{fig:model_outs}, with $1$ \,\unit{hr} aggregation.} 
    \label{fig:model_outs_1hr}
  \end{figure}
\end{center}

\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig2_12hr.png}
    \caption{As Figure \ref{fig:model_outs}, with $12$ \,\unit{hr} aggregation.} 
    \label{fig:model_outs_12hr}
  \end{figure}
\end{center}

\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig2_1day.png}
    \caption{As Figure \ref{fig:model_outs}, with $1$ \,\unit{day} aggregation.} 
    \label{fig:model_outs_1day}
  \end{figure}
\end{center}

\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig2_5day.png}
    \caption{As Figure \ref{fig:model_outs}, with $5$ \,\unit{day} aggregation.} 
    \label{fig:model_outs_5day}
  \end{figure}
\end{center}

\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig2_10day.png}
    \caption{As Figure \ref{fig:model_outs}, with $10$ \,\unit{day} aggregation.} 
    \label{fig:model_outs_10day}
  \end{figure}
\end{center}
\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig2_15day.png}
    \caption{As Figure \ref{fig:model_outs}, with $15$ \,\unit{day} aggregation.} 
    \label{fig:model_outs_15day}
  \end{figure}
\end{center}

>>>>

\subsection{Role of water discharge in sediment transport capacity}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{Fig2.pdf}
  \caption{Model outputs resulting from the hydrographs shown in panels a and e for the cases called \alpine (a-d) and \icesheet{} (e-h).". Gray (black) lines in a and e represent the subglacial channel size (water discharge).  In other panels, blue lines represent model outputs from the subglacial channel, while orange lines represent the subaerial channel.
    Data in plots are at $15$\unit{min} intervals.
    Arrows denote some events where the variable peaks in the subglacial channel prior to the subaerial one.
    Insets in e-h show the  peak melt event \icesheet{} denoted by shaded area.
    Note that the x and y axis are different for \alpine{} and \icesheet{} such that they each cover a summer.} 
  \label{fig:model_outs}
\end{figure}
Following the parameterizations defined in Sections~\ref{sect:sub_mode}~and~\ref{sect:fluv}, the water velocity, shear stress, and width-integrated shear stress exhibit different seasonal evolutions and peaks. Water velocity and shear stress represent the potential for sediment mobilization, and width-integrated shear stress represents the total sediment transport capacity across the channel bed (Figure~\ref{fig:model_outs}).

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\linewidth]{Fig3.png}
  \caption{Relationship between water discharge and velocity, shear stress, and width-integrated shear stress for \alpine{}  (a-c) and \icesheet (d-f). Variables have been normalized to mean values for better comparison amongst the model runs.
    $R_g$ ($R_f$) show the Spearman rank correlation values for the subglacial (subaerial) model outputs.
    Plots are shown at $15$\unit{min} interval.} 
  \label{fig:Qw_vari}
\end{figure}

@@

\begin{figure}[h]
  \centering
    \includegraphics[width=0.9\linewidth]{Fig4.png}
    \caption{Variance (measured by the standard deviation) in water velocity, shear stress and total shear stress for different time aggregations across a large number of subglacial and subaerial channel shapes and friction factors The subglacial (blue) and subaerial (orange) systems are distinguished as are \alpine{} (a-c) and \icesheet{} (d-f).
      Shaded areas denote the $25^{\mathrm{th}}$ and $75^{\mathrm{th}}$ quantiles of the $100$ parameter combinations tested for each of the systems (Section~\ref{sect:imp}).
      Solid lines denote  mean values.
      Time intervals shown with markers denote $15$\,\unit{min}, $1$\,\unit{hr}, $12$\,\unit{hr}, $1$\,\unit{d}, $5$\,\unit{d}, $10$\,\unit{d}, and $15$\,\unit{d} aggregation periods.
    } 
    \label{fig:multi_run}
  \end{figure}

@@

Considerations in interpretations of sediment discharge should be made given the findings presented here.
These considerations include:
\begin{enumerate}
\item the inconsistent relationship between water discharge and sediment transport capacity underneath glaciers;
\item the timing of peak sediment transport capacity below glaciers generally coincides with the large rates of change in water discharge, as opposed to the maximum quantity of water discharge;
\item the potentially increased variability in sediment discharge capacity from underneath glaciers than in rivers they feed;
\item the representations of water discharge such as subglacial sediment transport capacity, subglacial sediment access, or open channel processes near the glacier margin in sediment records collected near glaciers. 
\end{enumerate}

@@

\renewcommand{\figurename}{Figure S}
\setcounter{figure}{0}
\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig3_hr.png}
    \caption{As Figure \ref{fig:model_outs}, with $1$ \,\unit{hr} aggregation.} 
    \label{fig:model_outs_1hr}
  \end{figure}
\end{center}

\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig3_12hr.png}
    \caption{As Figure \ref{fig:model_outs}, with $12$ \,\unit{hr} aggregation.} 
    \label{fig:model_outs_12hr}
  \end{figure}
\end{center}

\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig3_1day.png}
    \caption{As Figure \ref{fig:model_outs}, with $1$ \,\unit{day} aggregation.} 
    \label{fig:model_outs_1day}
  \end{figure}
\end{center}

\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig3_5day.png}
    \caption{As Figure \ref{fig:model_outs}, with $5$ \,\unit{day} aggregation.} 
    \label{fig:model_outs_5day}
  \end{figure}
\end{center}

\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig3_10day.png}
    \caption{As Figure \ref{fig:model_outs}, with $10$ \,\unit{day} aggregation.} 
    \label{fig:model_outs_10day}
  \end{figure}
\end{center}
\begin{center}
  \begin{figure}[h]
    \includegraphics[width=0.7\linewidth]{Fig3_15day.png}
    \caption{As Figure \ref{fig:model_outs}, with $15$ \,\unit{day} aggregation.} 
    \label{fig:model_outs_15day}
  \end{figure}
\end{center}
